Keyword and Collocation analysis on India-related text of *Natural History*

### 2023-08-22 paper_quarto.qmd
0822 sequence adjust

Since the research focus is narrowed down to India-related text after the initial exploration, a dataset including all Indian place names mentioned in the text is extracted from the geographical-related text dataset. With a reference to *Barrington Atlas of the Greek and Roman World* (@talbert2000a, @talbert2000b), the approximate coordinates defining the Indian region during the time of *Natural Hisoty* are as follows[^3]:

@@

@@

```{r}
#| label: fig-col_keyword
#| tbl-cap:  Scatterplot of G_signed by absolute frequency

@@

**Geographical/Ethnic Group**: india, arabia, indian, ganges, indus, ethiopia, taprobane(G), thence, sail(A)

@@

**Precious Stone/Gem**: stones, amber, beryls, rock-crystal, glass, beryls(G)

@@

keyword_PMI_list <- data.frame(
  Word = c("ganges", "beryls", "ichthyophagi", "megasthenes", "obsidian", "bdellium", "agates", "callaina", "condensation", "gerra", "jomanes", "nonius", "prasii", "alia", "carnelian", "cophes", "hypasis", "merchandize", "peppertree", "sacae", "sandastros", "thornbush"),
  Exp = c("a major river in India", "a type of gemstone", "a group of people who primarily subsist on fish", "a Greek historian and diplomat", "a type of volcanic glass", "a fragrant resin obtained from certain trees", "a type of semiprecious gemstone", "pale green precious stone (lat)", "the process of vapor turning into a liquid state", "war (lat)", "a Roman nomen gentile, gens or \"family name\"", "a Roman nomen gentile, gens or \"family name\"", "prase, green coloured gem", "by another / different way / route (lat)", "a reddish-brown variety of chalcedony", "a river that rises in the ancient Paropamise range, eventually falling into the Indus river near its confluence with the Cophes river", "a river in north India", "goods or commodities", "a tree that produces peppercorns", "the easternmost nation of Elibe, situated to the south of Ilia and the north of Bern", "a precious stone found in India and Arabia", "any of many thorny or spiny shrubs and bushes"),
  Tag = c("river", "goods", "people", "people", "goods", "goods", "goods", "goods", "activity", "activity", "people", "people", "goods", "route", "goods", "river", "river", "goods", "tree", "river", "goods", "tree"),
  Sub_tag = c("N/A", "stone", "group of people", "famous people", "others", "others", "stone", "stone", "producing activity", "N/A", "human name", "human name", "stone", "N/A", "stone", "N/A", "N/A", "general", "origin of goods", "N/A", "stone", "N/A")
)

keyword_PMI_list %>% 
  as_tibble() %>%
  select(Word, Exp, Tag, Sub_tag) %>%                        
  kbl(col.names = c("Word", "Exp", "Category", "Sub_category")) %>% 
  kable_minimal()
```

@@

tag_counts <- keyword_PMI_list %>%
  count(Tag) %>%
  arrange(desc(n))

# Plot the tag distribution
ggplot(tag_counts, aes(x = n, y = reorder(Tag, -n), fill = Tag)) +
  geom_bar(stat = "identity") +
  labs(x = "Count", y = "Tag", fill = "Tag") +
  theme_minimal() +
  coord_flip()
```

@@

To analyse the textual collocating bi-gram of word "India", the `mclm::text_cooc()` function was employed, with "india" designated as the target item for the analysis. And following the same criteria as the previous keyword analysis, the collocation scores were filtered of having both PMI and G_signed scores of 2 or higher. By employing this approach, the prominent collocates of "india" were identified, providing a tangible understanding of the prevailing discourse and potentially reflecting Pliny the Elder's perspective on the region.

```{r}
#| label: tbl-coltable_PMI
#| tbl-cap-location: top
#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by PMI)
#| warning: false
#| echo: false

4.  $G^2$ signed highly overlapped with that of absolute frequency. (plot of corelation)

5.  list the overlapped keywords

6.  PMI sorting provides more information

>>>>

Since the research focus is narrowed down to India-related text after the initial exploration, a dataset including all Indian place names mentioned in the text is extracted from the geographical-related text dataset. With a reference to *Barrington Atlas of the Greek and Roman World* (@talbert2000, @talbert2000-1), the approximate coordinates defining the Indian region during the time of *Natural Hisoty* are as follows[^3]:

@@

To analyse the textual collocating bi-gram of word "India", the `mclm::text_cooc()` function was employed, with "india" designated as the target item for the analysis. Since the texual collocation of "India" is examinated, the span of the target word is set as the "textual units", to take the broader context into consideration.

And following the same criteria as the previous keyword analysis, the collocation scores were filtered of having both PMI and G_signed scores of 2 or higher. By employing this approach, the prominent collocates of "india" were identified, providing a tangible understanding of the prevailing discourse and potentially reflecting Pliny the Elder's perspective on the region.

```{r}
#| label: tbl-coltable_PMI
#| tbl-cap-location: top
#| tbl-cap: Top 20 collocates to the word "india" in Natural History (sorted by PMI)

Similar to the results of keyword analysis, the top 20 sorted list of absolute frequency and G singed have a 11/20 overlapped outputs. As shown in @fig-col_colloc, the signed G score and absolute frequency in textual collocation has a positibe correlation.

```{r}
#| label: fig-col_colloc
#| fig-cap: Correlation of signed G and absolute frequency in textual collocation

top_scores_colloc_df <- as_tibble(top_scores_colloc)

g1 <- top_scores_colloc_df %>%
  ggplot(aes(x = G_signed, y = a)) +
  labs(x = "signed G", y = "Absolute frequency") +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

g1
```

The high-ranking words of textual collocation with "India" in the work are cateforized as follows, those without specifying the association measurement are the overlapped ones:

**Geographical**: arabia, indian, ethiopia, ganges, indus(G)

**Numeric**: hundred, thousand(A), whole(A)

**Time**: year (A)

**Merchandise exchange**: mart(G)

**Precious Stone/Gem**: stones, rock-crystal, gems, pearls, gem(G), gemstone(G)

**Animal/Plant**: elephants, gum(A), lustre(G)

**Historical Figure**: alexander(A), megasthenes(G), onesicritus(G)

**Descriptive expression**: numerous(A), luxury(A), closely(A), valuable(A), bright(A), identical(G), smaragdus(G)

**Others**: shadow(A)

```{r}
coocs_ref_df <- as_tibble(coocs$ref_freqlist)
words_to_check_colloc <- c("arabia", "indian", "ethiopia", "ganges", "rock-crystal", "hundred", "elephants", "megasthenes", "indians", "gem", "lustre", "stones", "identical", "'smaragdus", "indus", "gems", "gemstone", "pearls", "onesicritus", "mart")
filtered_top_scores_colloc <- top_scores_colloc_df %>%
  filter(type %in% words_to_check_colloc)

abs_freq_lookup1 <- setNames(coocs_ref_df$abs_freq, coocs_ref_df$type)
nrm_freq_lookup1 <- setNames(coocs_ref_df$nrm_freq, coocs_ref_df$type)

results_colloc <- tibble(
  Word = filtered_top_scores_colloc$type,
  Target_Frequency = filtered_top_scores_colloc$a,
  Reference_Abs_Frequency = abs_freq_lookup1[filtered_top_scores_colloc$type],
  Reference_Nrm_Frequency = nrm_freq_lookup1[filtered_top_scores_colloc$type]
) %>% 
  kbl(col.names = c("Type", "Target_Frequency", "Reference_Abs_Frequency", "Reference_Nrm_Frequency")) %>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")

results_colloc

```
```{r}

words_to_check_colloc_pmi <- c(
  "megasthenes",
  "thorn-bush",
  "carnelian",
  "obsidian",
  "cophes",
  "merchandize",
  "mart",
  "expeditions",
  "patala",
  "arii",
  "ichthyophagi",
  "pursuits",
  "vermilion",
  "biggest",
  "onesicritus",
  "identical",
  "ganges",
  "engrave",
  "'smaragdus",
  "honey-coloured",
  "reflects"
)

filtered_top_scores_colloc <- top_scores_colloc_df %>%
  filter(type %in% words_to_check_colloc_pmi)

abs_freq_lookup1 <- setNames(coocs_ref_df$abs_freq, coocs_ref_df$type)
nrm_freq_lookup1 <- setNames(coocs_ref_df$nrm_freq, coocs_ref_df$type)

results_colloc_pmi <- tibble(
  Word = filtered_top_scores_colloc$type,
  Target_Frequency = filtered_top_scores_colloc$a,
  Reference_Abs_Frequency = abs_freq_lookup1[filtered_top_scores_colloc$type],
  Reference_Nrm_Frequency = nrm_freq_lookup1[filtered_top_scores_colloc$type]
) %>% 
  kbl(col.names = c("Type", "Target_Frequency", "Reference_Abs_Frequency", "Reference_Nrm_Frequency")) %>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")

results_colloc_pmi
```

@@

```{r}
#| label: fig-col_keyword
#| fig-cap: Scatterplot of G_signed by absolute frequency

@@

**Geographical**: india, arabia, indian, ganges, indus, ethiopia, taprobane(G), thence, sail(A)

@@

**Precious Stone/Gem**: stones, amber, rock-crystal, glass, beryls(G)

@@

keyword_PMI_list <- data.frame(
  Word = c("india", "ganges", "beryls", "indus", "taprobane", "ichthyophagi", "megasthenes", "obsidian", "bdellium", "agates", "callaina", "condensation", "expeditions", "gerra", "jomanes", "nonius", "patala", "prasii", "alia", "bactra", "carnelian", "ceylon", "cophes", "hypasis", "merchandize", "peppertree", "sacae", "sandastros", "thornbush"),
  Exp = c("name of the focused region of this study", "a major river in India", "a type of gemstone", "a major river in India", "Island in Sri Lanka", "a group of people who primarily subsist on fish", "a Greek historian and diplomat", "a type of volcanic glass", "a fragrant resin obtained from certain trees", "a type of semiprecious gemstone", "pale green precious stone (lat)", "the process of vapor turning into a liquid state", "referring to the expedition of Alexander the Great", "war (lat)", "name of a river", "a Roman nomen gentile, gens or \"family name\"", "refer to a city in Indian region", "prase, green coloured gem", "by another / different way / route (lat)", "name of a city in Asia Minor", "a reddish-brown variety of chalcedony", "name of an Island in Indian subcontinent", "a river that rises in the ancient Paropamise range, eventually falling into the Indus river near its confluence with the Cophes river", "a river in north India", "goods or commodities", "a tree that produces peppercorns", "the easternmost nation of Elibe, situated to the south of Ilia and the north of Bern", "a precious stone found in India and Arabia", "any of many thorny or spiny shrubs and bushes"),
  Category = c("region", "river", "goods", "river", "region", "people", "people", "goods", "goods", "goods", "goods", "activity", "activity", "activity", "river", "people", "region", "goods", "route", "region", "goods", "region", "river", "river", "goods", "plant", "river", "goods", "plant"),
  Remark = c("N/A", "N/A", "gemstone", "N/A", "N/A", "tribe", "referencing scholar", "other goods", "other goods", "gemstone", "gemstone", "producing activity", "N/A", "N/A", "N/A", "human name", "N/A", "gemstone", "N/A", "N/A", "gemstone", "N/A", "N/A", "N/A", "general goods", "origin of goods", "N/A", "gemstone", "N/A")
)

keyword_PMI_list %>% 
  as_tibble() %>%
  select(Word, Exp, Category, Remark) %>%                        
  kbl(col.names = c("Word", "Exp", "Category", "Remark")) %>% 
  kable_minimal()
```

@@

tag_counts <- keyword_PMI_list %>%
  count(Category) %>%
  arrange(desc(n))

# Plot the tag distribution
ggplot(tag_counts, aes(x = n, y = reorder(Category, -n), fill = Category)) +
  geom_bar(stat = "identity") +
  labs(x = "Count", y = "Category", fill = "Category") +
  theme_minimal() +
  coord_flip()
```

@@
